Modern Graph Generators: A Survey

### 2018-11-07 generators_SocialNetworks.tex
iThenticate modifications - part III (the rest)

\paragraph{S3G2} The Scalable Structure-correlated Social Graph Generator
(S3G2)~\cite{Pham2013} is a general framework which  generates a directed
labeled graph, where the nodes are objects with property values, and their
structure is determined by the class a node belongs to. S3G2 does not aim at
generating near real-world data, but at generating synthetic graphs with a
correlated structure. It causes that the probability to choose a certain
property value (from a pre-defined dictionary), or the probability to connect
two nodes with an edge are influenced by existing data values. For example, it
is possible to have a correlated degree distribution, from which the degree of
each node is generated, correlated with the properties of node. Hence the generator
can ensure that, e.g., people with many friends in a social network will
typically post more pictures than people with few friends, i.e., the amount of
friend nodes influences the amount of posted comment and picture nodes. The data generation process starts with generating a number of nodes with
property values generated according to specified property value correlations and
then adding respective edges according to specified correlation dimensions. It
has multiple phases, each focusing on one correlation dimension. Each pass along
one correlation dimension is a Map phase in which data is generated, followed by
a Reduce phase that sorts the data along the correlation dimension in the next
pass. A heuristic observation that ``the probability that two nodes are
connected is typically skewed with respect to some similarity between the
nodes'' enables to focus only on sliding window of most probable candidates. The core idea of the framework is demonstrated using an example of a social
network (consisting of persons and social activities).  The dictionaries for
property values are inspired by DBpedia and provided with 20 property value
correlations. The edges are generated according to 3 correlation dimensions.

@@

\paragraph{LDBC SNB} The Social Network Benchmark
(SNB)~\cite{Erling:2015:LSN:2723372.2742786} provided by LDBC consists of three
distinct benchmarks on a common dataset corresponding to three different
workloads. SNB models a social network akin to Facebook. The dataset consists of
persons and a friendship network that connects them; whereas the majority of the
data is in the messages that these persons post in discussion trees on their
forums. The three query workloads involve: (1) SNB-Interactive, i.e., complex
read-only queries, that touch a significant amount of data, (2) SNB-BI which
accesses a large percentage of all entities in the dataset and groups these in
various dimensions, and (3) SNB-Algorithms, i.e., graph analysis algorithms,
including PageRank, Community Detection, Clustering and Breadth First Search.
The graph generator realizes power laws, uses skewed value distributions, and
introduces plausible correlations between property values and graph structures.
It is implemented on top of Hadoop to provide scalability.

@@

\paragraph{Towards More Realistic Data} \cite{Nettleton2016} argued that the main body of existing work lies in
topology generation which approximates the characteristics of a real social
network (such as a small graph diameter, small average path length, skew degree
distribution, and community structures), however,  this is usually done without any data. Hence, they
introduced a general stochastic modeling system which allows the users to
populate a graph topology with data. The approach has three steps: (1) topology
generation (using R-MAT) plus community identification using the Louvain
method~\cite{1742-5468-2008-10-P10008} or usage of a real-world topology from
SNAP\footnote{\url{https://snap.stanford.edu/data/}}, (2) data definition
following distribution profiles, attribute value definitions, using a
parameterizable set of data propagation rules and affinities, and (3) data
population.

>>>>

\paragraph{S3G2} The Scalable Structure-correlated Social Graph Generator (S3G2)~\cite{Pham2013} is a general framework which produces a directed labeled graph whose vertices represent objects having property values. The respective classes determine the structure of the properties. S3G2 does not aim at generating near real-world data, but at generating synthetic graphs with a correlated structure. Hence, the existing data values influence the probability of choosing a certain property value from a pre-defined dictionary, or the probability of connecting two nodes. For example, the degree distribution can be correlated with the properties of a node and thus, e.g., people having many friend relationships typically post more comments and pictures. The data generation process starts with generating a number of nodes with property values generated according to specified property value correlations and then adding respective edges according to specified correlation dimensions. It has multiple phases, each focusing on one correlation dimension. Data is generated in a Map phase corresponding to a pass along one correlation dimension. Then the data are sorted along the correlation dimension in the following Reduce phase. A heuristic observation that ``the probability that two nodes are connected is typically skewed with respect to some similarity between the nodes'' enables to focus only on sliding window of most probable candidates. The core idea of the framework is demonstrated using an example of a social network (consisting of persons and social activities).  The dictionaries for property values are inspired by DBpedia and provided with 20 property value correlations. The edges are generated according to 3 correlation dimensions.

@@

\paragraph{LDBC SNB} Despite having a common Facebook-like dataset, thanks to three distinct workloads the Social Network Benchmark (SNB)~\cite{Erling:2015:LSN:2723372.2742786} provided by LDBC corresponds to three distinct benchmarks. The network nodes correspond to people and the edges represent their friendship and messages they post in discussion trees on their forums. The three query workloads involve: (1) SNB-Interactive, i.e., complex read-only queries accessing a significant portion of data, (2) SNB-BI, i.e., queries accessing a high percentage of  entities and grouping them in various dimensions, and (3) SNB-Algorithms, involving graph analysis algorithms, such as community detection, PageRank, BFS, and clustering. The graph generator realizes power laws, uses skewed value distributions, and ensures reasonable correlations between graph structures and property values. To provide scalability it is implemented on top of Hadoop.

@@

\paragraph{Towards More Realistic Data} \cite{Nettleton2016} argued that the main body of existing work lies in
topology generation which approximates the characteristics of a real social
network (such as a small graph diameter, skew degree
distribution, small average path length, and community structures), however,  this is usually done without any data. Hence, they
introduced a general stochastic modeling system which allows the users to
populate a graph topology with data. The approach has three steps: (1) topology
generation (using R-MAT) plus community identification using the Louvain
method~\cite{1742-5468-2008-10-P10008} or usage of a real-world topology from
SNAP\footnote{\url{https://snap.stanford.edu/data/}}, (2) data definition
following distribution profiles, attribute value definitions, using a
parameterizable set of data propagation rules and affinities, and (3) data
population.

### 2018-11-07 generators_analytics.tex
iThenticate modifications - part III (the rest)

\paragraph{HPC Scalable Graph Analysis Benchmark} The HPC Scalable Graph
Analysis Benchmark~\cite{HPCgraph,Bader:2005:DIH:2099301.2099360} represents an
application with multiple analysis techniques that access a single data
structure representing a weighted, directed graph. The benchmark is composed of
four separated operations (graph construction, classification of large vertex
sets, graph extraction with BFS, and graph analysis with betweenness centrality)
on a graph that follows a power-law distribution. The graph generator constructs a list of edge tuples containing vertex
identifiers (with the edge direction from the first one to the second one) and
weights that represent data assigned to the edges of the multigraph in the form
of positive integers with a uniform random distribution. The generator has the
following parameters: number of vertices, number of edges, and maximum weight of
an edge. The algorithm of the generator is based on R-MAT. Since the authors aim
to avoid data locality, in the final step the vertex numbers are randomly
permuted, and then edge tuples are randomly shuffled. A related project from the same authors developed for the 9th DIMACS Shortest
Paths Challenge is GTgraph~\cite{GTgraph}. It involves three types of graphs:
input graph instances used in the DARPA HPCS SSCA\#2 graph theory benchmark
(version 1.0), Erd\"{o}s-R\'{e}nyi random graphs, and small-world graphs based
on the R-MAT model.

>>>>

\paragraph{HPC Scalable Graph Analysis Benchmark} The HPC Scalable Graph Analysis Benchmark~\cite{HPCgraph,Bader:2005:DIH:2099301.2099360} consists of a weighted, directed graph that follows a power-law distribution and four related analysis techniques (namely graph construction, graph extraction with BFS, classification of large vertex sets, and graph analysis with betweenness centrality). The generator has the following parameters: number of vertices, number of edges, and maximum weight of an edge. It outputs a list of tuples containing identifiers of vertices of an edge (with the direction from the first one to the second one) and weights (positive integers  with a uniform random distribution) assigned to the edges of the multigraph.  The algorithm of the generator is based on R-MAT. To avoid data locality, in the final step the vertex numbers are randomly permuted and then the tuples are randomly shuffled. A related project from the same authors developed for the 9th DIMACS Shortest Paths Challenge is GTgraph~\cite{GTgraph}. It involves three types of graphs: (1) Erd\"{o}s-R\'{e}nyi random graphs, (2) input graph instances used in the DARPA HPCS SSCA\#2 graph theory benchmark (version 1.0), and (3) small-world graphs based on the R-MAT model.
